resistanceModelNotesAndy

### 2015-04-15 resistanceModelNotesAndy.Rmd
progress notes

Then in RStudio I had to set project options, build tools to package
(so maybe I should have done just done detools::setup())

@@

@@

1. can I create a plotting method that can accept multiple scenarios

1. look at the method used in the Barbosa paper
1. ask Ian if he has the code for the Barbosa classification trees analysis.

1. start to write script to run sensitivity analysis, does it want to work by creating a large input.csv file, or by setting input object directly.

@@

@@

### suggestion from Beth
a solution may be to provide a .csv file with the Curtis scenarios set up
and then the need to set the calibration number and params.csv in the R script can be removed altogether
the only bit of R code the user will need to change is the setwd() and the read.csv()

>>>>

Then in RStudio I had to set project options, build tools to package
(so maybe I should have done just done devtools::setup())

@@

emailed them to see about the error

**14/4/15** tue 11.45 - 14.15 2.5hrs 3-5.30 2.5 5hrs

can I create a plotting method that can accept multiple scenarios ?
initially it could just plot all scenarios as additional lines in the existing colours for locus & sex
use `plotallele.freq.andy`
might need to modify to accept more than one matrix of results outputs  
I thought tricky bit might be to set plot bounds based on multiple lines (but actually the y is already hardcoded from 0-1 for allele frequency). Might need to be a bit careful with x because different scenarios can have different numbers of generations.

done : fixed why `resistanceMaster()` currently fails. I suspect due to input scenario calibration combination, it used to work ??

Error in 1:ddt_cutoff : result would be too long a vector
In addition: Warning messages:
1: In data.matrix(mat) : NAs introduced by coercion
2: In min(which((amat[, r1col]) > 0.5)) :
  no non-missing arguments to min; returning Inf

the error comes from `plotcurtis_f2()`
I suspect it's because the input.parameters.csv isn't the one compatible with producing the curtis plot.
`plotcurtis_f2()` needs results matrices from 3 scenarios: 1 hch, 2 ddt, 3 combined. Yet the current csv I have in the package seems to have 7 scenarios
Input,Curtis Fig 2 Comb - calibration,DDT high,DDT high,DDT high,HCH high,HCH high,HCH high  
Why did it work before then ??
Aha! it's because in `createInputMatrix()` this sets up the 3 Curtis scenarios if an input file is not specified :
  `if( !params.csv && calibration == 1012 ){
    input <- matrix( ncol=3, nrow=52 )
    colnames(input) <- c("B (HCH)", "A (DDT)","Combination")`
So maybe I should have no input csv as the default.

setting params.csv=FALSE as the default for resistanceMaster() sorted it.

Back to `plotallele.freq.andy`, I might be able easily to modify it to accept a list of matrices for multiple scenarios, as well as it's current single scenario mode.

this gives me the number of generations per scenario
`sapply(listOut$results,nrow)`
70  70 160
`max_gen <- max( sapply(listOut$results,nrow) )`

done : create a plotting method that can accept multiple scenarios

now try to use it to plot a parameter range.
To run multiple scenarios one way would be to call `setInputOneScenario()` repeatedly to create single scenarios & then rbind these together into an input object that I can pass to `runModel()`

```{r}

input <- NULL
vals <- seq(0,1,0.2) #create a range of input values
for(i in vals)
{
 inputOneScenario <- setInputOneScenario( h.RS1_A0=i )  
 input <- cbind(input, inputOneScenario)
}

listOut <- runModel(input)
plotallele.freq.andy(listOut)

```
This is getting close to allowing the user to specify an input parameter and what range of that parameter you want to plot. I could then potentially create a UI allowing the user to do that.
Would it be useful to put the above code into a function ? 
Actually the above code is very close to what I would need for the sensitivity analysis.

I could create a `setInputMultiScenario()` function that accepts a vector of values for a param, and creates an input object with all other params set to their default. It could maybe even accept multiple args, but then would need to return the n*n scenarios. Also this is going away from the way that Ian suggested doing it by smapling from a distribution, maybe I should try that route first ?

In that case do I want to randomly change all params at once ?
Also might be good to get it to output a file at the end of each 100 runs, so that if it does crash during a long run, everything is not lost. These could just be RDA files saved from the listOut object.
Do I want it to output listOut() each time or will I process so that the outputs are smaller ?
(Might be better to keep the raw outputs to save any confusion later.)

The sensitivity analysis function may be called a bit like this :

```
#specify ranges for parameters, if a range is not specified the default will be used
#could offer option to setother params at diff fixed values
#this would only accomodate uniform distributions, OK for now
#think about random seeds later
#be careful about some params which must total one
input <- setInputSensiScenarios( n=100, h.RS1_A0=c(0,1) )
```

Am I reinventing the wheel here, can anything else help me with this ?

**15/4/15** wed 1.30-2.30 1hrs 3.45-

@@

1. see setInputSensiScenarios
1. start to write script to run sensitivity analysis, probably by creating a large input object rather than a large input.params.csv.

1. write a function to calculate timeToThreshold for all scenarios based on listOut, allow user to specify which locus.

1. ask Ian if he has the code for the Barbosa classification trees analysis.

@@

1. add some defensive checks, e.g. for sensible input variables

@@

### suggestion from Beth
a solution may be to provide a .csv file with the Curtis scenarios set up
and then the need to set the calibration number and params.csv in the R script can be removed altogether
